\documentclass[12pt]{report}
\author{Daniel de Jesús Sánchez Kelly}
\title{\bf Advanced Macroeconomics}
\date{Lecture Notes \\ El Colegio de México \\ \bigskip Stephen McKnight, PhD.}
                
\usepackage{formato}
\usepackage{booktabs}
\usepackage{circuitikz}
\usepackage{pgfplots}
\usepackage{graphics}
\pgfplotsset{width=7cm,compat=1.3}
\allowdisplaybreaks

\lhead{\textbf{Advanced Macroeconomics}}

\begin{document}

\maketitle
\tableofcontents
\pagebreak

\chapter*{Preliminary Notes}

This set of notes contains a detailed description -though definitely not extensive— of the main models used in modern macroeconomics. We cover almost all mathematical developments in detail, so that the reader can acquire a general perspective on how these models (and more advanced ones) are solved. Our primary objective is to offer Spanish-speaking students in the final year of their economics degree a resource not available in our language, which can serve to deepen or approach the study of macroeconomics. \\

We generally rely on two sources. On the one hand, the book \textit{Advanced Macroeconomics} by David Romer (2012), the central text in most intermediate-advanced level courses. Particularly in the final sections, we make use of other texts, although it is explicitly indicated when this is not the case. Secondly, and more importantly, the material used by Dr. Stephen McKnight for the course \textit{Advanced Macroeconomics}, of the 4th year of the Bachelor's Degree in Economics from the Center for Economic Studies of El Colegio de México. It is worth widely thanking Dr. McKnight for his direct and indirect contributions to this work. \\

There are 3 main sections in these notes. The first part (sections 1 to 4) goes over the 4 central macroeconomic growth models (Solow, Ramsey, OLG, and Endogenous Growth), which constitute the building blocks for the rest of the lectures. These are all micro-founded intertemporal models, useful for getting a grasp of macroeconomic modeling. \\

These notes are divided into 3 sections:
\begin{enumerate}
\item \textbf{Part 1} (Sections 1 to 4) details 4 economic growth models widely used in modern literature: The Solow Growth Model; the Ramsey Growth Model; the Overlapping Generations Model (OLG); and the Endogenous Growth Model. All of these are intertemporal models with micro-foundations, useful for the reader to acquire a general perspective on macroeconomic modeling.
\item \textbf{Part 2} (Sections 5 to 9) focuses on Business Cycle theory and its fluctuations, with special attention to fiscal and monetary policy. It also provides an introduction to the Neo-Keynesian synthesis.
\item \textbf{Part 3} (Sections 10 to 13) focuses on Open Economies, developing 4 intertemporal models concentrated on international trade, national accounts, and international financial asset markets.
\end{enumerate}

The content is intended to be self-contained, so most of the advanced mathematical tools required to derive conclusions from the models are detailed within the text itself. However, being aimed at advanced students, we assume familiarity with the basic tools of multivariable integral and differential calculus. Finally, the reader can address any questions related to these notes to the email: \textit{djsanchez@colmex.mx}.

\include{1. Solow/1-Solow.tex}

\include{2. Ramsey/2-Ramsey}

\include{3. OLG/3-OLG Model}

\end{document}

